Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-28 paper/main.tex
q equations

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vartist_a"] &  &             &  & {\Gamma(\gbase_a, \gfiber_a)} \arrow[lld, "g_a" description, dashed] \\
                                                                           &  & \dfiber_{c} &  &                                                                      \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vartist_b"] &  &             &  & Im_{\vartist_b} \in \gtotal \arrow[llu, "g_b" description, dashed]
\end{tikzcd}
\end{equation}

@@

\begin{equation}
  \label{eq:math:artist:diagram}
  \begin{tikzcd}
      \dtotal \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                            & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
      \end{tikzcd}
\end{equation}

@@

\subsection{Visualization Library Components}
\subsubsection{Graphic to Data: \vindex}
\begin{equation}
  \begin{tikzcd}
      \dtotal \arrow[d, "\pi"'] & \gtotal \arrow[d, "\pi"'] \\
      \dbase                   & \gbase \arrow[l, "\vindex"']
  \end{tikzcd}
  \label{eq:math:graphic:vindex}
\end{equation}

@@

\subsubsection{Data to Visual Encodings: \vchannel} %look at what K&S call these stages
Visual encoding functions \vindex\ are functors because they are expected to preserve structure on the data and visual side, as discussed in \autoref{sec:related-work:equivariance}.

@@

\begin{equation}
  \label{eq:math:artist:nu}
  \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}

We enforce the equivariance constraint specified in \autoref{eq:artist:construction:multi_nu} by constructing artists that apply \vchannel\ encoders such that 
\begin{equation}
  \label{eq:artist:construction:multi_nu}
  \begin{tikzcd}
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vchannel^{a}_{\dfiber_c}"] &  &                                                                                                                       &  & \vfiber^{a}_{\dfiber_c} \\
                                                                                          &  & \dfiber_{c} \arrow[rru, "\vchannel^{a}_{\dfiber_c}" description] \arrow[rrd, "\vchannel^{b}_{\dfiber_c}" description] &  &                         \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vchannel^{a}_{\dfiber_c}"] &  &                                                                                                                       &  & \vfiber^{b}_{\dfiber_c}
    \end{tikzcd}
\end{equation}

the same fiber in two different data sets run through the same $\vchannel_{i}$ encoder will output to the same set of visual values in the corresponding visual fiber $\vfiber_i$.

\subsubsection{Visual to Graphic: \vmark} % look at what K&S call these stages
Visual encodings to something like marks 
\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{diff_type_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

@@

\appendices
\section{Rendering: \gsection}
\section{Manufacturing $\vmarkd \leftarrow \vmark$}
\begin{equation}
  \begin{tikzcd}
      \textcolor{gray!50}{\dtotal} \arrow[r, "\vchannel", color=gray!50] \arrow[rd, "\pi"', color=gray!50] & \vtotal \arrow[d, "\pi"']                  & \vindex^*\vtotal \arrow[r, "\vmark", color=gray!50] \arrow[d, "\vindex^*\pi"'] \arrow[l,  "\vindex^*"'] & \textcolor{gray!50}{\gtotal} \arrow[ld, "\pi", color=gray!50] \\ & \dbase \arrow[u, "\vsection"', bend right] & \gbase \arrow[l, "\vindex"'] \arrow[u, "\vindex^*\vsection"', bend right]               &                          
      \end{tikzcd}
      \label{eq:math:artist:qhat}
\end{equation}

>>>>

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}[row sep = .5em]
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vartist_a"] &  &             &  & Im_{\vartist_a} \arrow[lld, "g_a" description, dashed] \\
                                                                           &  & \dfiber_{c} &  &                                                                      \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vartist_b"] &  &             &  & Im_{\vartist_b} \in \arrow[llu, "g_b" description, dashed]
\end{tikzcd}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:construction:all}
  \begin{tikzcd}
      \dtotal \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                            & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
      \end{tikzcd}
\end{equation}

@@

\subsection{Visualization Library Components}

\subsubsection{Graphic to Data: \vindex}
\begin{equation}
  \label{eq:artist:construction:xi}
  \begin{tikzcd}
      \dtotal \arrow[d, "\pi"'] & \gtotal \arrow[d, "\pi"'] \\
      \dbase                   & \gbase \arrow[l, "\vindex"']
  \end{tikzcd}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:construction:xi:multi_base}
  \begin{tikzcd}
    \dbase_{c} \arrow[d, hook] \arrow[r, hook] & \dbase_{b}                 & \gbase_b \arrow[l, "\vindex"]                                                \\
    \dbase_{a}                                 & \gbase_a \arrow[l, "\vindex"'] & \gbase_c \arrow[l, hook'] \arrow[u, hook] \arrow[llu, "\vindex" description]
  \end{tikzcd}
\end{equation}

Can be implemented in V

\begin{equation}
  \label{eq:artist:construction:xi:v}
  \begin{tikzcd}
  \textcolor{color=gray!50}{\dtotal}\arrow[rd, "\pi"', color=gray!50] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"', dashed] & \textcolor{color=gray!50}{\gtotal} \arrow[ld, "\pi", color=gray!50] \\
    & \dbase                   & \gbase \arrow[l, "\vindex"']                                                &                          
    \end{tikzcd}
\end{equation}

\subsubsection{Data to Visual Encodings: \vchannel} 
\begin{equation}
  \label{eq:artist:construction:nu}
\begin{tikzcd}
  \textcolor{gray!50}{\dtotal} \arrow[rd, "\pi"'] \arrow[r, "\vchannel"] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[d, "\vindex^*\pi"', color=gray!50] \arrow[l, "\vindex^*", color=gray!50] & \textcolor{gray!50}{\gtotal} \arrow[ld, "\pi", color=gray!50] \\
& \dbase                   & \textcolor{gray!50}{\gbase} \arrow[l, "\vindex"', color=gray!50]                                       &                          
  \end{tikzcd}
\end{equation}

Visual encoding functions \vindex\ are functors because they are expected to preserve structure on the data and visual side, as discussed in \autoref{sec:related-work:equivariance}.

@@

\begin{equation}
\label{eq:artist:construction:nu:fiber_map}
\begin{tikzcd}[column sep=.5em]
  \dfiber \arrow[rr, "\vchannel"] &                                                         & \vfiber \\
                                  & \dbase \arrow[lu, "\dsection"] \arrow[ru, "\vsection"'] &        
  \end{tikzcd}
\end{equation}

which means equivariance of 
\begin{equation}
\label{eq:artist:construction:nu:equivariance}
\begin{tikzcd}
  \dsection \arrow[d, "\varphi"'] \arrow[r, "\vchannel"] & \vsection \arrow[d, "\vchannel_{\varphi}"] \\
  \dsection^{\prime} \arrow[r, "\vchannel"]                       & \vsection^{\prime}                                 
  \end{tikzcd}
\end{equation}

But actually multiple variables please
\begin{equation}
  \label{eq:math:artist:nu}
  \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}

We enforce the equivariance constraint specified in \autoref{eq:artist:construction:multi_nu} by constructing artists that apply \vchannel\ encoders such that 
\begin{equation}
  \label{eq:artist:construction:multi_nu}
  \begin{tikzcd}[row sep=.5em]
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vchannel_{\dfiber_c}"]          &  &                                                                                                                        &  & \vfiber_{\dfiber_c}          \\
    &  & \dfiber_{c} \arrow[rru, "\vchannel_{\dfiber_c}" description] \arrow[rrd, "\vchannel^{\prime}_{\dfiber_c}" description] &  &                              \\
\dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vchannel^{\prime}_{\dfiber_c}"] &  &                                                                                                                        &  & \vfiber^{\prime}_{\dfiber_c}
    \end{tikzcd}
\end{equation}

\subsubsection{Visual to Graphic: \vmark} 
\begin{equation}
  \label{eq:artist:construction:q}
  \begin{tikzcd}
    \textcolor{gray!50}{\dtotal} \arrow[rd, "\pi"', color=gray!50] \arrow[r, "\vchannel", color=gray!50] & \textcolor{gray!50}{\vtotal} \arrow[d, "\pi", color=gray!50] & \vindex^*\vtotal \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"', color=gray!50] \arrow[r, "\vmark"] & \gtotal \arrow[ld, "\pi"] \\
    & \dbase & \gbase \arrow[l, "\vindex"', color=gray!50]                                            &                          
    \end{tikzcd}
\end{equation}

\begin{equation}
  \label{eq:artist:construction:q:xi}
  \begin{tikzcd}[column sep= 1em, row sep=.7em]
    \vtotal \arrow[rrd, "\hat{\vmark}"]                             &  &         \\
                                                                    &  & \gtotal \\
    \vindex^*\vtotal \arrow[uu, "\vindex^*"] \arrow[rru, "\vmark"'] &  &        
    \end{tikzcd}
\end{equation}

\begin{equation}
  \label{eq:artist:construction:q:fiber}
  \begin{tikzcd}[column sep=.5em]
    \vfiber \arrow[rr, "\vmark"] &                                                         & \gfiber \\
    & \gbase \arrow[ru, "\gsection"'] \arrow[lu, "\vsection"] &        
    \end{tikzcd}
\end{equation}
Visual encodings to something like marks

\begin{equation}
  \label{eq:artist:construction:q:equivariance}
  \begin{tikzcd}
    \vsection \arrow[d, "\vchannel_\varphi"'] \arrow[r, "\vmark"] & \gsection \arrow[d, "\vmark_\varphi"] \\
    \vsection^{\prime} \arrow[r, "\vmark"]                                 & \gsection^{\prime}                            
    \end{tikzcd}
\end{equation}

\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{diff_type_q.png}
  \caption{rework this as a commutative box w/ the r in E row associated w/ this qhat(k)}
\end{figure}

@@

\appendices
